---
title: "Lab 6"
author: "Gage Clawson"
date: "2/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(ggrepel)
library(ggspatial)
library(RColorBrewer)
library(raster)
library(plotly)

```

Goals:

- Read in spatial data
- Simplify polygons
- Add and transform projections (st_transform, st_crs)
- Create a bunch of maps
- Join spatial data
- Find intersections of spatial data
- Interactive plots
- Create sf from lat/lon coordinates


###Example 1. Dams in California

```{r}
ca_eco <- read_sf(".", layer ="ca_eco") %>%
  dplyr::select(US_L3NAME) %>%
  rename(Region = US_L3NAME) %>%
  st_simplify(dTolerance = 100) %>%
  st_transform(crs = 4326) 

```


```{r}
ca_counties <- read_sf(".", layer = "california_county_shape_file") 

st_crs(ca_counties) = 4326
```


```{r}
ca_dams <- read_sf(".", layer = "California_Jurisdictional_Dams") %>%
  rename(Condition = Condition_)

ca_dams$Condition <-fct_relevel(ca_dams$Condition, "Fair", "Satisfactory", "Unsatisfactory", "Poor")
```



Maps
```{r}
plot(ca_eco)
plot(ca_counties)
```

Make a map with ggplot:
```{r}

color_count <- 13

my_colors <- colorRampPalette(brewer.pal(10, "Set2"))(color_count)


ggplot(ca_eco) + 
  geom_sf(aes(fill = Region), 
          color = "NA", 
          show.legend = FALSE) +
  scale_fill_manual(values = my_colors) +
  geom_sf(data = ca_counties, 
          fill = "NA",
          color = "gray30", 
          size = 0.1) +
  geom_point(data = ca_dams, 
             aes(x = Longitude, y = Latitude),
             size = 1, 
             color = "gray10",
             alpha = 0.5) +
  theme_minimal() +
  coord_sf(datum = NA)

```

###Example 2. Dams in the Sierra Nevada eco-region

```{r}

sn <- ca_eco %>%
  filter(Region == "Sierra Nevada") %>%
  st_join(ca_dams)



ggplot(sn) +
  geom_sf(data = ca_counties, fill = "wheat3", color = "NA") + 
    geom_sf(fill = "lemonchiffon4", color = "NA") + 
    geom_point(aes(x = Longitude, y = Latitude), size = 0.5, color = "red4")
  

```

###Example 3. Eco-regions for Santa Barbara County
```{r}

sb <- ca_counties %>%
  filter(NAME == "Santa Barbara")


eco_clip <- st_intersection(ca_eco, sb)

ggplot(eco_clip) +
  geom_sf(data = ca_counties, fill = "gray90", color = "gray80", size = 0.2) +
  geom_sf(aes(fill = Region), color = "NA") + 
  scale_fill_manual(values = c("darkolivegreen2", "darkolivegreen", "gold2")) +
  coord_sf(xlim = c(-121, -119), ylim = c(33.5,35.5)) +
  geom_point(aes(x = -119.6982, y = 34.4208), size = 2) +
  geom_text(x = -119.6982, y = 34.35, label = "Santa Barbara") +
  theme_minimal() +
  theme(legend.position = c(0.5, 0.15))

```

###Example 4. Intro to interactive plots with tmap

```{r}

tmap_mode("view")
map_sb_eco <- tm_shape(eco_clip) +
  tm_fill("Region", palette = "RdPu", alpha = 0.5) + 
  tm_shape(ca_counties) +
  tm_borders()

map_sb_eco

# Example with a different Basemap
tm_basemap("CartoDB.DarkMatter") +
  tm_shape(eco_clip) + 
  tm_borders(col = "white")
```

###Example 5. Fault Lines

```{r}
fault_lines <- read_sf(".", layer = "GMC_str_arc") %>%
  st_transform(crs = 4326) %>%
  separate(LTYPE, into = c("syn_ant", "certainty", "direction"), sep =",")

plot(fault_lines)

ggplot() +
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) +
  theme_void()


# Fault lines in sb county:
sb_faults <- fault_lines %>%
  st_intersection(sb)

ggplot() +
  geom_sf(data = sb) +
  geom_sf(data = sb_faults, aes(color = syn_ant)) +
  theme_minimal()

tm_basemap("Esri.NatGeoWorldMap") + 
  tm_shape(sb) +
  tm_borders(col = "gray50", lwd = 2) +
  tm_shape(sb_faults) + 
  tm_lines(col = "syn_ant", palette = c("orange", "purple"), lwd = 2)
   
```

###Example 6. Faceted maps

```{r}

ggplot() + 
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) + 
  facet_wrap(~syn_ant)

```

###Example 7. Making spatial points

```{r}
ca_sites <- read_csv("cadfw_sensitive_sites.csv")


sites_sf <- st_as_sf(ca_sites, coords = c("LONDD", "LATDD"), 
    crs = 4326, agr = "constant") 

ggplot() + 
  geom_sf(data = ca_counties, fill = "gray40") + 
  geom_sf(data = sites_sf, aes(color = PRI_CODE), size = 0.3)
```


###Example 8. Chloropleth of CA counties by NUMBER of dams in each county

```{r}
intersection <- st_intersection(ca_dams, ca_counties)

dams_per_county <- intersection %>%
  group_by(NAME) %>%
  tally()

ca_tot <- ca_counties %>%
  st_join(dams_per_county) %>%
  dplyr::select(NAME.x, n) %>%
  rename(name = NAME.x)


ca_tot$n[is.na(ca_tot$n)] <- 0 
```



```{r}
ggplot() +
  geom_sf(data =ca_tot, aes(fill = n), size = 0.2) +
  theme_minimal() +
  scale_fill_continuous(low = "yellow", high = "red")



```


